Pillar 1 - Sequential Pattern Mining

### 2019-02-13 Pillar 1 - Sequential Pattern Mining.Rmd
debuggs to match both "rule" and "rules" as variable

    # separate rule
    mutate(
      rules = str_remove_all(rules, pattern = "[<]|[{]|[}]|[>]")
      ) %>%
    separate(
      rules,
      into = c("lhs", "rhs"),
      sep = " = "
      ) %>%

>>>>

    # separate rule
    rename_at(
      vars(matches("rule")),
      function(x) substr(x, 1, 4)
    ) %>%
    mutate(
      rule = str_remove_all(rule, pattern = "[<]|[{]|[}]|[>]")
      ) %>%
    separate(
      rule,
      into = c("lhs", "rhs"),
      sep = " = "
      ) %>%
